Normalized expressions

### 2021-03-11 analysis/normalized.Rmd
Numbers for 1st 12 minimzed expressions

Minimized:
```{r}
widespread_minimized <- E_cano %>%
  group_by(minimized) %>%
  summarize(n_call_sites = n_distinct(src_ref), proportion = ratio(n_call_sites, nb_call_sites), n_packages = n_distinct(ev_package), n_operations = round(mean(n_op, na.rm=TRUE), 2), percent_envir = round(100 * sum(!is.na(envir)) / n(), 2))

widespread_minimized %>%
  arrange(desc(n_call_sites)) %>%
  datatable()
```

>>>>

Minimized:
```{r}
widespread_minimized <- E_cano %>%
  group_by(minimized) %>%
  summarize(n_call_sites = n_distinct(src_ref), proportion = ratio(n_call_sites, nb_call_sites), n_packages = n_distinct(ev_package), n_operations = round(mean(n_op, na.rm=TRUE), 2), percent_envir = ratio(sum(!is.na(envir)), n())) %>% 
  arrange(desc(n_call_sites))

widespread_minimized %>%
  datatable()
```

```{r}
nrows <- 12
r_vec("MinimizedCallSites", nrows, pull(widespread_minimized, n_call_sites))
r_vec("MinimizedPropSites", nrows, pull(widespread_minimized, proportion))
r_vec("MinimizedPackage", nrows, pull(widespread_minimized, n_packages))
r_vec("MinimizedOperations", nrows, pull(widespread_minimized, n_operations))
r_vec("MinimizedPercentEnvir", nrows, pull(widespread_minimized, percent_envir))
```
